\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[]{amsthm} %lets us use \begin{proof}
\usepackage[]{amssymb} %gives us the character \varnothing
\usepackage[]{amsmath}
\usepackage[parfill]{parskip} %avoid indent when skipping lines
\usepackage{mathtools}
\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
	linkcolor=blue,
	filecolor=magenta,      
	urlcolor=cyan,
	pdftitle={18.100A-ps5},
	pdfpagemode=FullScreen,
}
%\urlstyle{same}

\title{18.100A Assignment 5}
\author{Octavio Vega}
\date\today

\begin{document}
\maketitle

\section*{Problem 1}
\begin{proof}
	We have that
	\begin{equation}
		L = \lim\limits_{n\to\infty} \frac{|x_{n+1}-x|}{|x_n-x|} < 1.
	\end{equation}
	Then for every $\epsilon > 0$, $\exists N \in \mathbb{N}$ such that $\forall n \geq N$, 
	\begin{equation}
		\left|\frac{x_{n+1}-x}{x_n - x}\right| - 1 < \epsilon.
	\end{equation}
	Rearranging gives
	\begin{equation}
		|x_{n+1}-x| < (1+\epsilon)|x_n - x|.
	\end{equation}
	By taking $\epsilon$ to be arbitrarily small, we have, $\forall n \geq N$,
	\begin{equation}
		\xRightarrow{\epsilon \to 0} |x_{n+1}-x| < |x_n-x|.
	\end{equation}
	Define $y_n := |x_n - x|$. Then $\forall n \geq N$, 
	\begin{equation}
		0 \leq y_{n+1} < y_n,
	\end{equation}
	so $\{y_n\}_n$ is a decreasing sequence bounded below by $0$. Hence,
	\begin{align}
		&\implies y_n \rightarrow 0 \\
		&\implies |x_n - x| \rightarrow 0 \\
		&\implies x_n \rightarrow x.
	\end{align}
	Therefore, $\{x_n\}_n$ converges to $x$.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Problem 2}
\subsection*{(a)}
Let $x_n = \frac{(-1)^n}{n}$. Then $\forall n \in \mathbb{N}$,
\begin{equation}
	-\frac{1}{n} \leq x_n \leq \frac{1}{n}.
\end{equation}
Allowing $n \to \infty$ on all sides of the inequality gives
\begin{equation}
	0=\lim\limits_{n\to\infty} \left(-\frac{1}{n}\right) \leq \lim_{n \to \infty} x_n \leq \lim_{n\to\infty} \left(\frac{1}{n}\right)=0.
\end{equation}
So by the Squeeze Theorem, $\lim_{n\to\infty} x_n = 0$. Finally, by the theorem from lecture 9, we conclude that $\lim\inf{x_n}=\lim\sup{x_n}=0$.

\subsection*{(b)}
Let $x_n = (-1)^n\frac{(n-1)}{n}$. Define
\begin{equation}
	a_n := \sup\{x_k \;|\; k\geq n\} \textrm{, and } b_n := \sup\{x_k \;|\; k\geq n\}.
\end{equation}
Then $\forall n \in \mathbb{N}$, we have 
\begin{align}
	|x_n| &= \left|\frac{n-1}{n}\right| \cdot |(-1)^n| \\
	&= \frac{n-1}{n} \\
	&= 1-\frac{1}{n} \\
	&\leq 1.
\end{align}
Thus, $x_n$ is bounded and $-1\leq x_n \leq 1$. 

Let $n_k=2k$ and $m_k=2k-1$ for $k\in\mathbb{N}$. Then we construct two subsequences $\{x_{n_k}\}_k$ and $\{x_{m_k}\}_k$ of $\{x_n\}_n$ via
\begin{equation}
	x_{n_k} := \frac{2k-1}{2k}(-1)^{2k} = \frac{2k-1}{2k},
\end{equation}
and
\begin{equation}
	x_{m_k} := \frac{2k-2}{2k-1}(-1)^{2k-1} = \frac{2-2k}{2k-1}.
\end{equation}
Taking the limit of the first subsequence gives 
\begin{equation}
	\lim_{k \to \infty} x_{n_k} = \lim_{k \to\infty} \left(1-\frac{1}{2k}\right) = 1,
\end{equation}
and for the second subsequence we get
\begin{equation}
	\lim_{k\to\infty} x_{m_k} = \lim_{k \to \infty}\left(\frac{1}{2k-1}-1\right)=-1.
\end{equation}
Thus, $\{x_{n_k}\}_k$ converges to $1$, and $\{x_{m_k}\}_k$ converges to $-1$. Then \\$\sup\{x_k \;|\; k\geq n\} \geq 1$. But $-1\leq x_n \leq 1$, so it must also be true that
\begin{equation}
	\sup\{x_k \;|\; k\geq n\} \leq \sup x_n = 1.
\end{equation}
Thus, $\sup\{x_k \;|\; k\geq n\}=1$, and we can conclude that $\lim\sup x_n =1$.

Similarly, $\inf\{x_k \;|\; k\geq n\}\leq -1$, but $-1\leq x_n \leq 1$, so we must have
\begin{equation}
	\inf \{x_k \;|\; k\geq n\} \geq \inf x_n = -1,
\end{equation}
so $\inf \{x_k \;|\; k\geq n\}=1$. Therefore, we conclude also that $\liminf x_n = -1$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Problem 3}
\begin{proof}
	(i) Since $x_n \leq y_n \forall n\in\mathbb{N}$, then for each $n$, we have
	\begin{equation}\label{sup-leq-sup}
		\sup \{x_k \;|\; k\geq n\} \leq \sup \{y_k \:|\; k\geq n\}.
	\end{equation}
	Taking the limit on both sides of \eqref{sup-leq-sup} gives
	\begin{equation}
		\xRightarrow{n\to\infty} \limsup x_n \leq \limsup x_n,
	\end{equation}
	as desired.
	
	(ii) Since $x_n \leq y_n \forall n \in \mathbb{N}$, then for each $n$, we have
	\begin{equation}\label{inf-leq-inf}
		\inf\{x_k \;|\; k\geq n\} \leq \inf \{y_k \;|\; k\geq n\}.
	\end{equation}
	Taking the limit in \eqref{inf-leq-inf} yields
	\begin{equation}
		\xRightarrow{n \to\infty} \liminf x_n \leq \liminf y_n,
	\end{equation}
	and we are done.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Problem 4}
\subsection*{(a)}
\begin{proof}
	Since $\{x_n\}_n$ and $\{y_n\}_n$ are bounded sequences, then $\exists B_0 \geq 0$ and $B_1 \geq 0$ such that $\forall n \in \mathbb{N}$, $|x_n| \leq B_0$ and $|y_n| \leq B_1$.
	
	Choose $B = B_0 + B_1$. Then by the triangle inequality,
	\begin{equation}
		|x_n + y_n| \leq |x_n| + |y_n| \leq B_0 + B_1 = B.
	\end{equation}
	Therefore, the sequence $\{x_n + y_n\}_n$ is bounded.
\end{proof}

\subsection*{(b)}
\begin{proof}
	Let $\{x_{n_k}\}_k$ be a subsequence of $\{x_n\}_n$. Since the sequence $\{x_n\}_n$ is bounded, then $\{x_{n_k}\}_k$ must also be bounded. Then by the Bolzano-Weierstrass theorem, $\exists$ a (sub) subsequence $\{x_{n_{k_i}}\}_i$ of the subsequence $\{x_{n_k}\}_k$ such that $\{x_{n_{k_i}}\}_i$ converges; i.e. that $\lim_{i\to\infty} x_{n_{k_i}}$ exists. Then
	\begin{equation}
		\liminf x_n \leq \lim_{i\to\infty} x_{n_{k_i}}.
	\end{equation}
	By the same logic as above, $\exists$ a (sub-sub) subsequence $\{y_{n_{k_{i_l}}}\}_l$ of $\{y_{n_{k_i}}\}_i$ such that $\lim_{l\to\infty} y_{n_{k_{i_l}}}$ exists. Then
	\begin{equation}
		\liminf y_n \leq \lim_{l \to \infty} y_{n_{k_{i_l}}}.
	\end{equation}
	Thus the corresponding subsequence $\{x_{n_{k_{i_l}}} + y_{n_{k_{i_l}}}\}_l$ of $\{x_{n_k} + y_{n_k}\}_k$ is convergent, and 
	\begin{equation}
		\lim_{l\to\infty}\left(x_{n_{k_{i_l}}} + y_{n_{k_{i_l}}}\right) = \lim_{k\to\infty} x_{n_k} + \lim_{k\to\infty} y_{n_k}.
	\end{equation}
	But we also have
	\begin{align}
		\lim_{l\to\infty}\left(x_{n_{k_{i_l}}} + y_{n_{k_{i_l}}}\right) &= \lim_{l\to\infty} x_{n_{k_{i_l}}} + \lim_{l\to\infty} y_{n_{k_{i_l}}}\\
		&= \lim_{i \to \infty} x_{n_{k_i}} + \lim_{l\to\infty} y_{n_{k_{i_l}}} \\
		& \geq \liminf x_n + \liminf y_n.
	\end{align}
	Additionally,
	\begin{equation}
		\liminf (x_n + y_n) \geq \lim_{l\to\infty}\left(x_{n_{k_{i_l}}} + y_{n_{k_{i_l}}}\right).
	\end{equation}
	Therefore, $\liminf x_n + \liminf y_n \leq \liminf (x_n + y_n)$. 
\end{proof}

\subsection*{(c)}
Let $x_n = (-1)^n$ and $y_n = (-1)^{n+1}$ for $n \in \mathbb{N}$. Then
\begin{equation}
	x_n + y_n = (-1)^n + (-1)^{n+1} = (-1)^n (1-1) = 0.
\end{equation}
Thus, $\liminf (x_n + y_n) = 0$. But $\liminf x_n = \liminf y_n = -1$, so 
\begin{equation}
	\liminf x_n + \liminf y_n = -1 - 1 = -2 < 0.
\end{equation}
Therefore this example demonstrates a case where equality does not hold for the theorem in the previous sub-problem. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Problem 5}
\begin{proof}
	($\Rightarrow$) Suppose $\lim_{n\to\infty} x_n = 0$.
	
	Let $a_n = \sup \{|x_k| \;|\; k\geq n\}$. By \href{https://github.com/ovega14/RealAnalysis_solutions/blob/main/PS3/18.100A_ps3.pdf}{PS3.4}, since $a_n$ is a supremum, then $\forall n$ $\exists x_n$ such that $a_n - \frac{1}{n} < |x_n| \leq a_n$; i.e.
	\begin{equation}
		-\frac{1}{n} < |x_n|-a_n \leq 0.
	\end{equation}
	It becomes clear from the equation above that by the squeeze theorem, \\$\lim_{n\to\infty}(|x_n| - a_n)=0$, hence
	\begin{equation}
		0=\lim_{n\to\infty}|x_n|=\lim_{n\to\infty}a_n = \limsup |x_n|,
	\end{equation}
	as desired.
	
	($\Leftarrow$) Suppose $\limsup |x_n|=0$. Then $\lim_{n\to\infty} \sup\{|x_k| \;|\; k\geq n\}$ = 0.
	
	Let $a_n = \sup\{|x_k| \;|\; k\geq n\}$. Then by definition of the supremum, we have
	\begin{equation}
		0 \leq |x_n| \leq a_n.
	\end{equation}
	Taking the limit as $n\to\infty$ in the above inequality yields
	\begin{equation}
		0 \leq \lim_{n\to\infty}|x_n|\leq \limsup |x_n|=0.
	\end{equation}
	Thus, by the squeeze theorem, $|x_n|\rightarrow 0$.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Problem 6}
\textbf{Claim:} There does not exist any sequence $\{x_n\}_n$ such that $\liminf x_n = -1$, $\lim_{n\to\infty}x_n=0$, and $\limsup x_n=1$.
\begin{proof}
	Suppose $\{x_n\}_n$ is a sequence such that $x_n \rightarrow 0$. Then $\{x_n\}_n$ converges.
	
	Now suppose $\liminf x_n = -1$ and $\limsup x_n = 1$. Thus,
	\begin{equation}
		\liminf x_n \neq \limsup x_n.
	\end{equation}
	Then by the theorem from lecture, $\{x_n\}_n$ does not converge. $(\Rightarrow \Leftarrow)$. This is a contradiction to the assumption that the sequence is convergent, so our initial assumption that such a sequence existed must be incorrect.
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Problem 7}
\begin{proof}
	Let $\epsilon_0 > 0$. Since $\{x_n\}_n$ is a Cauchy sequence, then $\exists N_0 \in \mathbb{N}$ such that $\forall n\geq N_0 + 1$,
	\begin{equation}
		|x_n - x_{n-1}| < \epsilon_0.
	\end{equation}
	Now let $\epsilon_1 = |x_n - x_{n-1}|$. Then since $\{x_n\}_n$ is Cauchy, $\exists N_1 \in \mathbb{N}$ such that
	\begin{equation}
		|x_{n+1}-x_n| < \epsilon_1.
	\end{equation} 
	Choose $M=N_1$. Then $\forall n \geq M$, 
	\begin{equation}
		|x_{n+1}-x_n| < |x_n - x_{n-1}|,
	\end{equation}
	as desired.
\end{proof}

\end{document}